---
title: "Opt_3_analysis_script"
author: "moaraj"
date: "2/24/2017"
output:
  pdf_document: default
  html_document: default
---
Detach all the packes that are loaded from the CRAN
```{r}
lapply(paste('package:',names(sessionInfo()$otherPkgs),sep=""),detach,character.only=TRUE,unload=TRUE)
```

load all the libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(reshape2)
library(ggplot2)
library(plyr)
library(readr)
library(tidyr)
library(vioplot)
library(ggthemes)
```

Import Annotated Files, Tranposed, all commas, spaces and semi colons removed in notepad++. 
INSERT The metab data catagories in the to first row
```{r}
Data_Curated_Annotations <- read.csv(file = "moaraj_opt_3.csv")
Data_Curated_Annotations_transpose <- read.csv(file = "moaraj_opt_3_transpose.csv")

metab_data <- Data_Curated_Annotations_transpose
metab_data_names <- c("Index", "Extraction", "Mouse", "Strain", "Diet", "Sex", 
                      as.character(Data_Curated_Annotations$name))

names(metab_data) <- metab_data_names
metab_data <- metab_data[-which(duplicated(names(metab_data)))]

metab_data <- metab_data %>% 
  dplyr::mutate_each_(., funs = funs(as.factor), 
                      vars = c("Index", "Extraction", "Mouse", "Strain", "Diet", "Sex")) 
```


Add indexes for replicaites using the mod function on the sample index
```{r}
metab_data <- merge(metab_data %>% mutate(replicate  = paste("rep_", rep(c(1,2), times = dim(metab_data)[1]/2), sep = "")) %>% select(Index, replicate), metab_data, by = "Index")
#zou need to have unqiue values in the bz mere
#can be done by selecting multiple columns
```

Perform Summary Statistics on the Mouse Level
```{r}
#pdf(file = "TIC_Summary_Statistics.pdf")
strain_box_TIC <- ggplot(data = metab_data, 
                  aes(x = metab_data$Strain, 
                  y = rowMeans(metab_data[,8:ncol(metab_data)])))

strain_box_TIC + geom_point() + geom_boxplot(outlier.color = "red") +
                 labs(list( x = "BXD Mouse Strain", y = "Ion Current a.u.")) +
                 theme_minimal() +
                 theme(axis.text.x=element_text(angle=90, hjust=1), 
                 plot.background = element_rect(fill = "white"),
                 panel.grid.major.y = element_line(colour = "grey"))

ggsave("strain_box_TIC.pdf", width = 5, height = 5, dpi = 100) 


mouse_box_TIC <- ggplot(data = metab_data,
                 aes(x = metab_data$Mouse, 
                 y = rowMeans(metab_data[,8:ncol(metab_data)])))

mouse_box_TIC +  geom_point() + geom_boxplot(outlier.color = "red") + 
                 labs(list(x = "Mouse Ear Tag Number", y = "Ion Current a.u.")) +
                 theme_minimal() +
                 theme(axis.text.x=element_text(angle=90, hjust=1), 
                 plot.background = element_rect(fill = "white"),
                 panel.grid.major.y = element_line(colour = "grey"),
                 panel.background = element_rect(colour = "grey", size=1, fill=NA, linetype = "solid"))


                 ggsave("mouse_box_TIC.pdf", width = 5, height = 5, dpi = 100) 


rep_box_TIC <- ggplot(data = metab_data, 
                      aes(x = metab_data$replicate, 
                          y = rowMeans(metab_data[,8:ncol(metab_data)])))

rep_box_TIC + geom_point() + geom_boxplot(outlier.color = "red") + 
              labs(list(x = "Freeze Thaw Replicates", y = "Ion Current a.u.")) +
              theme_minimal() +
              theme(axis.text.x=element_text(angle=0, hjust=1), 
              plot.background = element_rect(fill = "white"),
              panel.grid.major.y = element_line(colour = "grey"))

ggsave("rep_box_TIC.pdf", width = 5, height = 5, dpi = 100) 
```


Perform Summary Statistics on the Metabolite Level
```{r}

blank_data <- filter(metab_data, Mouse == "Blank")
blank_data_filtered <- blank_data[1:200]
blank_data_index <- 1:ncol(blank_data_filtered)

TIC_Blank = NULL
TIC_Blank = ggplot(melt(blank_data_filtered), aes(x=variable, y=value, col=Mouse)) 
TIC_Blank + geom_boxplot() + theme(axis.text.x=element_text(angle=90, hjust=1)) +
            labs(list(x = "Metabolite Index", y = "Ion Current a.u.")) +
            theme_minimal() +
            theme(axis.text.x=element_text(angle=90, hjust=1), 
            plot.background = element_rect(fill = "white"),
            panel.grid.major.y = element_line(colour = "grey"))

ggsave("TIC_Blank_.pdf", width = 30, height = 10, dpi = 200) 


TIC_Blank_log <- NULL
TIC_Blank_log <- ggplot(melt(blank_data), aes(x=variable, y= log(value), col=Mouse)) 
TIC_Blank_log + geom_boxplot() + theme(axis.text.x=element_text(angle=90, hjust=1))
TIC_Blank_log + labs(title = "") + xlab("Effect of Freeze Thaw") + ylab("Ion Current a.u.")
ggsave("TIC_Blank_log.pdf", width = 30, height = 10, dpi = 200) 

TIC_all_mice <- NULL
TIC_all_mice <- ggplot(melt(metab_data), aes(x=variable, y=value, col=Mouse)) 
TIC_all_mice + geom_point() + theme(axis.text.x=element_text(angle=90, hjust=1))
TIC_all_mice + labs(title = "") + xlab("Effect of Freeze Thaw") + ylab("Ion Current a.u.")
ggsave("TIC_all_mice_point.pdf", width = 30, height = 10, dpi = 200)

TIC_all_mice <- NULL
TIC_all_mice <- ggplot(melt(metab_data), aes(x=variable, y=log(value), col=Mouse)) 
TIC_all_mice + geom_point() + theme(axis.text.x=element_text(angle=90, hjust=1)) 
TIC_all_mice + labs(title = "") + xlab("Effect of Freeze Thaw") + ylab("Ion Current a.u.")

ggsave("TIC_all_mice_point_log.pdf", width = 30, height = 10, dpi = 200) 
```


```{r}
blank_rank <- blank_data
blank_rank$rowMeans <- (rowMeans(blank_data[8:ncol(blank_data)]))
plot(sort(blank_rank$rowMeans))

metab_rank <- filter(metab_data, Mouse != "Blank")

blank_col_rank <- colMeans(blank_data[8:ncol(blank_data)])[1:300]
metab_col_rank <- colMeans(metab_data[8:ncol(metab_data)])[1:300]
average_col_error <- sqrt((metab_col_rank - blank_col_rank)^2)

Error_data <- cbind(blank_col_rank, metab_col_rank)
Error_data_melt <- melt(Error_data)

pdf(file = "ion_current.pdf", width = 5, height = 5)
plot(sort(metabj_col_rank), type = "l", log = "y", 
     #main = "Average Metabolite ION Currents", 
     xlab = "Metabolite Number",
     ylab = "Ion Current a.u")
  
    lines(sort(blank_col_rank), col = "red", type = "l")
    lines(sort(   sqrt((metab_col_rank[-301] - blank_col_rank)^2)   ), type = "l", col = "blue")
dev.off()

pdf
Error_Plot <- ggplot(Error_data_melt, 
              aes(x = c(1:300, 1:300),
                  y=(sort(value)), 
                  col=Var2)) + annotation_logticks()

Error_Plot + geom_point()




```





